Spatial Reasoning and Statistical Graphics

### 2014-11-06 Paper/Draft1/TestingVisualAptitude.Rnw
Add example lineups

\documentclass[10pt,journal,compsoc]{IEEEtran}
%---------------------------------------------------
% TVCG packages and header
% *** CITATION PACKAGES ***
%
\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  \usepackage[nocompress]{cite}
\else
  % normal IEEE
  \usepackage{cite}
\fi
% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage{graphicx}
  % declare the path(s) where your graphic files are
  \graphicspath{{Figure/}{Images/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  \DeclareGraphicsExtensions{.pdf,.jpg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% *** MATH PACKAGES ***
%
\usepackage[cmex10]{amsmath}
\usepackage{amssymb}

@@

qplot(data=lineup.type.sum3, 
      x=testscore, y=lineup.pct, geom="jitter", colour=I("grey30")) + 
  geom_smooth(method="lm") + 
  facet_grid(lineup.type~testtype, scales="free") + 
  ylab("Proportion of Lineups Correct") + 
  xlab("Test Score")+
  geom_text(data=cor.labels, aes(x=x, y=1.1, label=label), hjust=0, vjust=1, size=3) + 
  theme_bw() + 
  theme(legend.position="bottom", legend.direction="horizontal", 
        axis.text.x=element_text(angle=30, hjust=1),
        plot.margin=unit(c(0,0,0,0),"mm"))
@
\end{document}

>>>>

\documentclass[10pt,journal,compsoc]{IEEEtran}
%---------------------------------------------------
% TVCG packages and header
% *** CITATION PACKAGES ***
%
\ifCLASSOPTIONcompsoc
  % IEEE Computer Society needs nocompress option
  % requires cite.sty v4.0 or later (November 2003)
  \usepackage[nocompress]{cite}
\else
  % normal IEEE
  \usepackage{cite}
\fi
% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage{graphicx}
  % declare the path(s) where your graphic files are
  \graphicspath{{Figure/}{Images/}{../../Images/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  \DeclareGraphicsExtensions{.pdf,.jpg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% *** MATH PACKAGES ***
%
\usepackage[cmex10]{amsmath}
\usepackage{amssymb}

@@

qplot(data=lineup.type.sum3, 
      x=testscore, y=lineup.pct, geom="jitter", colour=I("grey30")) + 
  geom_smooth(method="lm") + 
  facet_grid(lineup.type~testtype, scales="free") + 
  ylab("Proportion of Lineups Correct") + 
  xlab("Test Score")+
  geom_text(data=cor.labels, aes(x=x, y=1.1, label=label), hjust=0, vjust=1, size=3) + 
  theme_bw() + 
  theme(legend.position="bottom", legend.direction="horizontal", 
        axis.text.x=element_text(angle=30, hjust=1),
        plot.margin=unit(c(0,0,0,0),"mm"))
@
\section{Lineup Task Examples}
\subsection{Lineup Set 1}
\comment{Description of original purpose of the experiment}
\begin{figure}[htbp]
\includegraphics[keepaspectratio=T,width=.9\linewidth]{../../Images/Lineups1/boxplot_1_15_5_4_13}
\caption{Boxplots used to compare the two distributions.}
\end{figure}
\begin{figure}[htbp]
\includegraphics[keepaspectratio=T,width=.9\linewidth]{../../Images/Lineups1/density_1_15_5_4_13}
\caption{Density plots used to compare the two distributions.}
\end{figure}
\begin{figure}[htbp]
\includegraphics[keepaspectratio=T,width=.9\linewidth]{../../Images/Lineups1/dotplot_1_15_5_4_13}
\caption{Dotplots used to compare the two distributions.}
\end{figure}
\begin{figure}[htbp]
\includegraphics[keepaspectratio=T,width=.9\linewidth]{../../Images/Lineups1/histogram_1_15_5_4_13}
\caption{Histograms used to compare the two distributions.}
\end{figure}
\FloatBarrier
\subsection{Lineup Set 2}
\comment{Description of original purpose of the experiment. Note that this experiment appears to have more outliers.}
\begin{figure}[htbp]
\includegraphics[keepaspectratio=T,width=.9\linewidth]{../../Images/Lineups2/file147f94f6965d7}
\caption{Boxplots.}
\end{figure}
\begin{figure}[htbp]
\includegraphics[keepaspectratio=T,width=.9\linewidth]{../../Images/Lineups2/file147f9e65f0e4}
\caption{Boxplots with jittered points.}
\end{figure}
\begin{figure}[htbp]
\includegraphics[keepaspectratio=T,width=.9\linewidth]{../../Images/Lineups2/file147f9fc58d73}
\caption{Bee swarm boxplots.}
\end{figure}
\begin{figure}[htbp]
\includegraphics[keepaspectratio=T,width=.9\linewidth]{../../Images/Lineups2/file147f93acbb7e4}
\caption{Violin plots.}
\end{figure}
\FloatBarrier
\subsection{Lineup Set 3}
\comment{Description of original purpose of the experiment.}
\begin{figure}[htbp]
\includegraphics[keepaspectratio=T,width=.9\linewidth]{../../Images/Lineups3/file13876a225d34-single}
\caption{QQ Plot with guide line.}
\end{figure}
\begin{figure}[htbp]
\includegraphics[keepaspectratio=T,width=.9\linewidth]{../../Images/Lineups3/file13877c93dc78-single}
\caption{QQ Plot with acceptance bands.}
\end{figure}
\begin{figure}[htbp]
\includegraphics[keepaspectratio=T,width=.9\linewidth]{../../Images/Lineups3/file13878e5c92f-single}
\caption{QQ Plot rotated 45 degrees.}
\end{figure}
\end{document}
